---
title: "R Notebook"
output: html_notebook
---

# __Statistical tests for association__

__Fisher's exact test__

__Data__

| Allele | A | G |||||||||
|:------|:-----:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|
| Case | 10  | 12 |||||||||
| Control | 66  | 26  |||||||||           

```{r}
fisher.test(matrix(c(12, 10, 26, 66), nrow=2))
```


¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡


__Dominent model__

| Allele | AA | *G |||||||||
|:------|:-----:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|
| Case | 5  | 6 |||||||||
| Control | 23  | 23  |||||||||           
    


__Recessive model__

| Allele | A* | GG |||||||||
|:------|:-----:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|-------:|
| Case | 5  | 6 |||||||||
| Control | 43  | 3  |||||||||           
    


```{r}
fisher.test(matrix(c(6, 5, 23, 23), nrow=2))
```

```{r}
fisher.test(matrix(c(6, 5, 3, 43), nrow=2))

```





¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡


__Pearson's Chi-squared test__
```{r}
chisq.test(matrix(c(6, 5, 3, 43), nrow=2))
```

```{r}
chisq.test(matrix(c(6, 5, 23, 23), nrow=2))
```






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡


__Cochran-Armitage Trend Test__

```{r}
library(SNPassoc)
library(coin)
data(SNPs)
SNPs[1:10, 1:10]
```





```{r, echo=FALSE, fig.width=200, message=FALSE, warning=FALSE}
library(knitr)
kable(SNPs[1:10, 1:10])
```





```{r}
datSNP <- setupSNP(SNPs,6:40,sep="")
xtabs(~ casco + snp10001, data=datSNP)
```



```{r}
independence_test(casco~snp10001, data=datSNP, teststat="quad", scores=list(snp10001=c(0,1,2)))
```






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡

__HWE(Hardy-Weinberg Equilibrium) test__
```{r}
library(SNPassoc)
data(SNPs)
pre_SNPs<-snp(SNPs$snp10005,sep="")
summary(pre_SNPs)
```

```{r}
plot(pre_SNPs, label="snp10005", col="red")
```



```{r}
myData<-setupSNP(data=SNPs,colSNPs=6:40,sep="")
res<-tableHWE(myData)
head(res, n=10)

```

```{r}
SNPs[,8]
```

```{r}
res<-tableHWE(myData,strata=myData$sex)
head(res, n=10)
```






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡

__MANHATTAN Plot__


```{r}
library(qqman)
head(gwasResults, n=6)
```
```{r, echo=FALSE}
kable(head(gwasResults, n=6))
```

```{r}
manhattan(gwasResults, main = "Manhattan Plot", cex = 0.5, cex.axis = 0.8, col = c("blue4", "orange3"))
```






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡


#Rare variant association test

```{r}
library(seqMeta)
data(seqMetaExample)

?seqMetaExample
```

```{r}
dim(Z1)
```
```{r}
Z1[1:5,1:5]
```
```{r}
Z2[1:5,1:5]
head(pheno1)
head(pheno2)
```



__Burden test__
```{r}
cohort1 <- prepScores(Z=Z1, y~1, SNPInfo=SNPInfo, data=pheno1)
cohort2 <- prepScores(Z=Z2, y~1, SNPInfo=SNPInfo, data=pheno2)
out <- burdenMeta(cohort1, cohort2, SNPInfo = SNPInfo, mafRange=c(0, 0.01))

out$p
which(out$p < 0.05)
```
¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



__SKAT test__¡¡¡¡¡¡¡¡¡¡

Sequence Kernel Association Test

```{r}
cohort1 <- prepScores(Z=Z1, y~sex+bmi, SNPInfo = SNPInfo,data =pheno1)
cohort2 <- prepScores(Z=Z2, y~sex+bmi, SNPInfo = SNPInfo,kins=kins, data=pheno2)
out.skat <- skatMeta(cohort1, cohort2, SNPInfo = SNPInfo)
out.skat[ order(out.skat$p), ]
```

¡¡¡¡¡¡¡¡¡¡
```{r, echo=FALSE}
kable(head(out.skat[ order(out.skat$p), ]))
```












¡¡¡¡¡¡¡¡¡¡






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




__SKAT-O test__¡¡¡¡¡¡¡¡¡¡¡¡¡¡¡¡¡¡¡¡



```{r}
out.skat <- skatOMeta(cohort1, cohort2, SNPInfo = SNPInfo)
out.skat[ order(out.skat$p), ]
```
```{r, echo=FALSE}
kable(head(out.skat[ order(out.skat$p), ]))
```
¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡

¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡






¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡




¡¡¡¡¡¡¡¡¡¡



¡¡¡¡¡¡¡¡¡¡


